Racial and Ethnic Differences in ETI: Outcomes

### 2024-08-05 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
ugh, okay better paths again

```{r setup}
#| include: false
# Libraries
library(tidyverse)
library(gtsummary)
library(ggflowchart)
library(lmerTest)
library(splines)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

>>>>

```{r setup}
#| include: false
# Libraries
library(tidyverse)
library(gtsummary)
library(ggflowchart)
library(lmerTest)
library(splines)
# Paths
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/tim/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```
